A decision support tool for the Home Health Care Routing and Scheduling Problem

### 2021-10-25 tex/Paper/combined_table_aith_results.tex
files for paper.
updated citations and format.

\begin{table}[htbp!]
\centering
    \caption{Performance of the best and average results found by GRASP DST compared with the three algorithms presented in \cite{AitHaddadene2016} (ILS, \emph{ah\_ils}, basic GRASP,  \emph{ah\_grasp}, and GRASPxILS, \emph{ah\_gi}) for the three instance groups \emph{G1}, \emph{G2} and \emph{G3}.}
    \begin{tabular}{cccccc}
    \label{tab:group_table_aith_combined}\\\hline

Result  &   Group   &   \emph{ah\_ils}  &   \emph{ah\_grasp}    &   \emph{ah\_gi}   &   \emph{GRASP}    \\  \hline
\multicolumn{6}{l}{\emph{Best}} \\                                              
    &   \emph{G1}   &   38.16   &   \textbf{38.04}  &   \textbf{38.04}  &   \textbf{38.04}  \\  
    &   \emph{G2}   &   -97.83  &   -97.54  &   -99.57  &   \textbf{-99.69} \\  
    &   \emph{G3}   &   -251.35 &   -231.54 &   -245.42 &   \textbf{-251.55}    \\  
\multicolumn{6}{l}{\emph{Avg.}} \\                                              
    &   \emph{G1}   &   42.27   &   38.39   &   38.05   &   \textbf{38.04}  \\  
    &   \emph{G2}   &   -91.85  &   -94.04  &   -97.91  &   \textbf{-99.19} \\  
    &   \emph{G3}   &   -240.82 &   -226.79 &   -239.44 &   \textbf{-247.01}    \\  
    \hline
    \end{tabular}
\end{table}

>>>>

\begin{table}[htbp!]
\centering
    \caption{Performance of the best and average results found by GRASP DST compared with the three algorithms presented in \citet{aithaddadene2016} (ILS, \emph{ah\_ils}, basic GRASP,  \emph{ah\_grasp}, and GRASPxILS, \emph{ah\_gi}) for the three instance groups \emph{G1}, \emph{G2} and \emph{G3}. Figures in bold indicate the best results for each instance group. \comp{Should rename \textit{GRASP} so that it is clear that it is the algorithm from this paper.}}
    \begin{tabular}{cccccc}
    \toprule
Result  &   Group   &   \emph{ah\_ils}  &   \emph{ah\_grasp}    &   \emph{ah\_gi}   &   \emph{GRASP}    \\  \midrule
\multicolumn{6}{l}{\emph{Best}} \\                                              
    &   \emph{G1}   &   38.16   &   \textbf{38.04}  &   \textbf{38.04}  &   \textbf{38.04}  \\  
    &   \emph{G2}   &   -97.83  &   -97.54  &   -99.57  &   \textbf{-99.69} \\  
    &   \emph{G3}   &   -251.35 &   -231.54 &   -245.42 &   \textbf{-251.55}    \\  
\multicolumn{6}{l}{\emph{Average}} \\                                              
    &   \emph{G1}   &   42.27   &   38.39   &   38.05   &   \textbf{38.04}  \\  
    &   \emph{G2}   &   -91.85  &   -94.04  &   -97.91  &   \textbf{-99.19} \\  
    &   \emph{G3}   &   -240.82 &   -226.79 &   -239.44 &   \textbf{-247.01}    \\  
    \bottomrule
    \end{tabular}
\label{table:grouptableaithcombined}
\end{table}
